---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hence.plots

<!-- badges: start -->
<!-- badges: end -->

The goal of hence.plots is to provide easy to use table and plot functions in the 
standards of Hence Analytics.

## Installation

You can install the development version of hence.plots from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rodrigo-pifano/hence.plots")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hence.plots)
library(data.table)
library(magrittr)
library(plotly)
```

### 1) Table

```{r}
mtcars %>%
  hence_table(p_row_names = TRUE)

```

<br><br/>

### 2) Histogram

```{r}
hence_histogram(mtcars$mpg,
                p_title = "Histogram example",
                p_xlab = "X label test",
                p_ylab = "counts") 
```

<br><br/>

### 3) Line Charts {.tabset .tabset-fade}

#### Single 

```{r}
hence_line_chart(p_dados = mtcars,
                 p_x = hp,
                 p_y = mpg,
                 p_title = "Line chart example") 
```

<br><br/>

#### Grouped

```{r}
hence_line_chart(p_dados = mtcars %>% mutate(am = as.factor(am)),
                 p_x = hp,p_y = mpg,
                 p_color = am,
                 p_title = "Grouped line chart example") 
```

<br><br/>

### 4) Other types

Bar plot

```{r}
mtcars %>%
  ggplot(aes(x = am,y = disp)) +
  geom_bar(stat = "identity") +
  theme_hence()
```

<br><br/>

Density plot

```{r}
mtcars %>%
  ggplot(aes(x = mpg)) +
  geom_density() +
  theme_hence()
```


<br><br/>

There is also the possibility of customizing certain parameters of theme_hence():

```{r}
mtcars %>%
  ggplot(aes(x = am,y = disp)) +
  geom_bar(stat = "identity", fill = "dark green") +
  theme_hence(p_base_size = 20,
              p_pase_family = "Times New Roman",
              p_line_colour = "blue")
```

<br><br/>
